|

### 2021-03-12 documentation/readme.Rmd
Remove token from README image
Prepared for clean compilation

---
output: github_document
---

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png?token=AI2VF2PMPYJQ277S7LBU4ILAJOPVI"></center>

>>>>

---
output:
  github_document:
    html_preview: false
---

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>
